\newpage
\section{Conclusion}
%本来想造火箭，结果只能拧个螺丝钉
In this project, we conducted a thorough investigation in the research area concerning the weighted model counting approach for Probabilistic Inference. The critical process of the project was the CNF encoding of Bayesian Networks. We have implemented Four encoding schemes, and we have shown that when dealing with networks with large local structure, the CNF encoding combined with weighted model counting perform remarkably better than the well-known junction tree algorithm regardless of the high treewidth. We did experiment with both Bayesian benchmarks and Bayesian networks generated from real-world examples. We compare the results based on different encoding schemes and also with the junction tree algorithm.\\

\noindent One of the difficulties for this project was the understanding of research papers. The research papers contained a lot of logic formulas, and some of the simplification steps were not clearly mentioned in the paper. Another difficulty was the implementation process since nearly no online resource is available that the whole project and data structure was designed on our own. 

\noindent Success has been achieved was the extension of QM algorithm that performs simplification for multi-variable logical forms, and the extension of Pgmpy library so that the method support fetching parameter values through indexing that is much faster than the original method with Variable-Elimination class.\\

\noindent In summary, great results have been achieved.
