\newpage
\appendix
\section*{Appendix}
\subsection{File Structure}
The Git repository contains the folder, some of the benchmarks and some testing results. The source code for encoding is in the subfolder Bayesian \_V1. To run the encoding, open main.py. Before running the encoding, we need to change the file path in line 198 to point to the .bif file we want to encode. \\
\begin{itemize}
    \item enc1\_simplified\_2(Bayesian Network) encode the Bayesian network using Simplified Full Encoding.
    \item enc2\_simplified\_2(Bayesian Network) encode the Bayesian network using Improved Encoding.
    \item encode\_3(Bayesian Network) encode the Bayesian network using Group encoding.
\end{itemize}

\noindent Some of the benchmarks are stored under Ratio\_50, Ratio\_75 and Ratio\_90. It also contains some of the Compiled NNF file with and extension '.cnf.nnf'.

\subsection*{Pgmpy and QM}
The link to download Pgmpy is \url{https://github.com/pgmpy/pgmpy}. To run the code, the folder need to be added to the project.\\

The link to download QM is \url{http://robertdick.org/python/qm-0.2.tar.gz}. After downloading the file, unzip it and copy the qm.py to the project.


\subsection*{Running miniC2D}
To download the model counter, go to page \textcolor{blue}{http://reasoning.cs.ucla.edu/minic2d/download.php}\\
To run the model counter, go to the downloaded folder.
\begin{lstlisting}
$ cd bin/darwin
For model counting
$ ./miniC2D -c <path to the CNF file> - C
\end{lstlisting}
A sample output of Model Counting:\\
\noindent\rule{15cm}{0.4pt}
\begin{lstlisting}
CNF stats: 
  Vars=36 / Clauses=92
  CNF Time	0.000s
Constructing vtree (from primal graph)...Wrong cut! 2 1
Wrong cut! 3 2
  DONE
Vtree stats:
  Vtree widths: con<=4, c_con=44 v_con=4
  Vtree Time	0.003s
Compiling... DONE
  NNF memory      	11.5 KB
  Learned clauses      	1
Cache stats:
  hit rate   	43.8%
  lookups    	32
  ent count  	18
  ent memory 	0.9 KB
  ht  memory 	152.6 MB
  clists     	1.0 ave, 1 max
  keys       	4.1b ave, 8.0b max, 2.0b min
  Compile Time	0.000s
Saving compiled NNF to file... DONE
  Save Time       	0.001s
NNF stats:
  Nodes           	281
  Edges           	418
Post compilation
  Loading NNF from file... DONE
  Load Time       	0.000s
NNF stats:
  Nodes           	281
  Edges           	418
  Counting... 128 models / 0.000s
Total Time: 0.114s
\end{lstlisting}
\noindent\rule{15cm}{0.4pt}